scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex

>>>>

Tomographic images often suffer from artifacts or poor signal-to-noise
ratio. Several denoising filters are available for image restoration,
from general-purpose filters such as median and bilateral filters, to more
specific filters. Total-variation denoising~\citep{Chambolle2004,
Getreuer2012} is well-suited to restore
piecewise-constant images, such as images with a small number of phases
encountered in materials science~\citep{Bouttes2015}. Conversely, images
with a fine-grained texture are better preserved with non-local means
denoising~\citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
